---
title: "Systems"
author: "Marie JULLIEN"
format: html
editor: visual
---

## Question 2
Link to my github repository: https://github.com/mariejullien/Systems.git

## Question 3
```{r}
#| message: false
library(here)
library(vroom)
library(dplyr)
library(tidyr)
```

```{r}
here::i_am("JULLIEN.qmd")
```


```{r}
imaginarystars <- vroom(here("Data","List+sytems.csv"),
                        locale = locale(decimal_mark = ","))
```
The number of star system is `r nrow(imaginarystars)`.
The number of row correspond to the number of star systems. 
The number of star system is `r ncol(imaginarystars)`.
We have 8 columns which is the number of variables. 

```{r}
str(imaginarystars)
```

We notice that the variables relative mass, radius and luminosity are of type characte, however they should be numerical so we modify the variables. 

```{r}
imaginarystars <- imaginarystars %>%
  mutate(`RELATIVE MASS` = ifelse(is.na(`RELATIVE MASS`), NA, as.numeric(`RELATIVE MASS`)),
         radius = ifelse(is.na(radius), NA, as.numeric(radius)),
         Luminosity = ifelse(is.na(Luminosity), NA, as.numeric(Luminosity)))

```

## Question 4
```{r}
nb_obs_with_missing <- imaginarystars %>%
  summarise(Nb_obs_with_missing = sum(rowSums(is.na(.)) > 0))

datades <- data.frame(
  Nb_column = nrow(imaginarystars),
  Nb_variables = ncol(imaginarystars),
  Nb_missingvaluesStar_idx=sum(is.na(imaginarystars$Star_idx)),
  Nb_missingvaluesStarName=sum(is.na(imaginarystars$STAR_NAME)),
  Nb_missingvaluesdistance=sum(is.na(imaginarystars$DISTANCE)),
  Nb_missingvaluesEqtemp=sum(is.na(imaginarystars$`equivalent temperature`)),
  Nb_missingvaluesrelativemass=sum(is.na(imaginarystars$`RELATIVE MASS`)),
  Nb_missingvaluesradiusx=sum(is.na(imaginarystars$radius)),
  Nb_missingvaluesluminosity=sum(is.na(imaginarystars$Luminosity)),
  Nb_missingvaluesstartype=sum(is.na(imaginarystars$`star type`)),
  Nb_obs_with_missing = as.vector(t(nb_obs_with_missing))
)


knitr::kable(datades)

```
```{r}
datades_long <- datades |>
  pivot_longer(cols = everything(), names_to = "Variable", values_to = "Value")
knitr::kable(datades_long)
```
For the data to be more readable I pivot in long format. 









