---
title: "Systems"
author: "Marie JULLIEN"
format: html
editor: visual
---

## Question 2
Link to my github repository: https://github.com/mariejullien/Systems.git

## Question 3
```{r}
#| message: false
library(here)
library(vroom)
library(dplyr)
```

```{r}
here::i_am("JULLIEN.qmd")
```


```{r}
imaginarystars <- vroom(here("Data","List+sytems.csv"),
                        locale = locale(decimal_mark = "."))
```
The number of star system is `r nrow(imaginarystars)`.
The number of row correspond to the number of star systems. 
The number of star system is `r ncol(imaginarystars)`.
We have 8 columns which is the number of variables. 

```{r}
str(imaginarystars)
```

We notice that the variables relative mass, radius and luminosity are of type characte, however they should be numerical so we modify the variables. 

```{r}
imaginarystars <- imaginarystars %>%
 mutate(`RELATIVE MASS` = as.numeric(`RELATIVE MASS`),
         radius = as.numeric(radius),
         Luminosity = as.numeric(Luminosity))
```

